---
html_document: default
author: "Wei"
date: '2024-09-26'
output:
  html_document:
    df_print: paged
title: "receiver operating characteristic curve (ROC curve)"
---

# 1. loading library and function
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ROCR))
suppressPackageStartupMessages(library(pROC))
suppressPackageStartupMessages(library(caret))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(ggbeeswarm))
suppressPackageStartupMessages(library(pacman))
pacman::p_load(tidyverse,ggpubr,rstatix,ggsci,ggsignif,reshape2)
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(pheatmap))
options(dplyr.summarise.inform = FALSE)

```


# 2. loading data
```{r}
Clinical <- read_rds("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/31_Clinical_information/GC_Clinical_info_20240925.rds")

data_feature <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/00_backup/20240618-all-features.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(data_feature)[colnames(data_feature)=="GCID"] <- "Sample"

cv1 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv1.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv1)<-c("predicted", "predicted_prob", "actual", "Sample")
cv2 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv2.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv2)<-c("predicted", "predicted_prob", "actual", "Sample")
cv3 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv3.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv3)<-c("predicted", "predicted_prob", "actual", "Sample")
cv4 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv4.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv4)<-c("predicted", "predicted_prob", "actual", "Sample")
cv5 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv5.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv5)<-c("predicted", "predicted_prob", "actual", "Sample")
cv6 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv6.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv6)<-c("predicted", "predicted_prob", "actual", "Sample")
cv7 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv7.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv7)<-c("predicted", "predicted_prob", "actual", "Sample")
cv8 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv8.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv8)<-c("predicted", "predicted_prob", "actual", "Sample")
cv9 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv9.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv9)<-c("predicted", "predicted_prob", "actual", "Sample")
cv10 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/cv10.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(cv10)<-c("predicted", "predicted_prob", "actual", "Sample")
Training_dataset <- bind_rows(cv1, cv2, cv3, cv4, cv5, cv6, cv7, cv8, cv9, cv10)

IVD_data <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/Internal_val.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(IVD_data) <- c("predicted", "predicted_prob", "actual", "Sample")
EVD_data <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/External_val.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(EVD_data) <- c("predicted", "predicted_prob", "actual", "Sample")
join_data <- bind_rows(Training_dataset, IVD_data, EVD_data) %>% 
  distinct()

```


# 3. data processed
## 3.1 join
```{r}
join_data_Clinical <- join_data %>% 
  left_join(Clinical, by = c("Sample" = "Sample")) %>% 
  dplyr::mutate(Group_predicted = case_when(predicted == 0 ~ "Non-GC",
                                            predicted == 1 ~ "GC",
                                  )) %>% 
  distinct()

join_data_feature <- join_data_Clinical %>%
  left_join(data_feature, by = c("Sample" = "Sample")) %>%
  distinct()

```


## 3.2 calculate wilcox between Non-GC and GC, and select significant features 
```{r}
data_feature_all <- join_data_feature %>% 
  select(Group_predicted, F1:F8716)
# write.table(test_join_data_feature, "test_join_data_feature.txt", sep = "\t", row.names = F)

# 获取除了'Group_predicted'之外的所有列名
features <- setdiff(names(data_feature_all), "Group_predicted")

# 初始化一个空的数据框来存储结果
data_feature_wilcox <- data.frame(Feature = character(),
                                  P_Value = numeric(),
                                  Median_NonGC = numeric(),
                                  Median_GC = numeric(),
                                  stringsAsFactors = FALSE)

# 遍历每个特征进行Wilcoxon检验
for (feature in features) {
    # 选择Non-GC和GC组的数据
    group_NonGC <- data_feature_all[data_feature_all$Group_predicted == "Non-GC", feature]
    group_GC <- data_feature_all[data_feature_all$Group_predicted == "GC", feature]
    
    # 计算中位数
    median_NonGC <- median(group_NonGC, na.rm = TRUE)
    median_GC <- median(group_GC, na.rm = TRUE)

    # 进行Wilcoxon秩和检验
    test_result <- wilcox.test(group_NonGC, group_GC, exact = FALSE)

    # 保存结果到数据框
    data_feature_wilcox <- rbind(data_feature_wilcox, data.frame(Feature = feature,
                                         P_Value = test_result$p.value,
                                         Median_NoGC = median_NonGC,
                                         Median_GC = median_GC,
                                         Fold_Change = median_NonGC/median_GC))
}


data_feature_wilcox2 <- data_feature_wilcox %>% 
  filter(P_Value < 0.001) %>% 
  arrange(P_Value)


write.csv(data_feature_wilcox2, "data_feature_wilcox.csv", row.names = FALSE, col.names = TRUE)

```


# 10. End Motif (Top 100 features)
## 10.1 colname
```{r}
EndMotif <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/Feature_names.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(EndMotif) <- c("Feature_num", "Feature_chr", "Type")

EndMotif2 <- EndMotif %>% 
  filter(Type == "Endmotif")

```

## 10.2 data_Endmotif
```{r}
# join_data_feature %>%
#   group_by(OS_time) %>%
#   summarise(count = n())

data_Endmotif <- join_data_feature %>% 
  dplyr::select(Group_predicted, F1285, F1366, F1468, F1337, F1251, F1411)
colnames(data_Endmotif) <- c("Group_predicted", "CACT", "GCGC", "TTTT", "CTTA", "AGCC", "TACG")

# write.table(data_Endmotif, "data_Endmotif.txt", sep = "\t", row.names = F)

```


# 11. data_Endmotif plot
```{r}
summary(data_Endmotif[data_Endmotif$Group_predicted=="Non-GC",]$CACT)
summary(data_Endmotif[data_Endmotif$Group_predicted=="GC",]$CACT)
p <- wilcox.test(data_Endmotif[data_Endmotif$Group_predicted=="Non-GC",]$CACT, data_Endmotif[data_Endmotif$Group_predicted=="GC",]$CACT)
p$p.value

# Reshape data from wide to long format
data_long <- pivot_longer(data_Endmotif, cols = c(CACT, GCGC, TTTT, CTTA, AGCC, TACG), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("CACT.Non-GC", "CACT.GC", 
                                           "GCGC.Non-GC", "GCGC.GC", 
                                           "TTTT.Non-GC", "TTTT.GC", 
                                           "CTTA.Non-GC", "CTTA.GC", 
                                           "AGCC.Non-GC", "AGCC.GC", 
                                           "TACG.Non-GC", "TACG.GC"))

# Create a list for pairwise comparisons
comparison_list <- list(c("CACT.Non-GC", "CACT.GC"), 
                        c("GCGC.Non-GC", "GCGC.GC"),
                        c("TTTT.Non-GC", "TTTT.GC"), 
                        c("CTTA.Non-GC", "CTTA.GC"),
                        c("AGCC.Non-GC", "AGCC.GC"), 
                        c("TACG.Non-GC", "TACG.GC"))

pdf("20240926_cfDNA_10_Endmotif_boxplot_v1.pdf", height=4, width=10)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.5, color = "black", size = 4) + 
  theme_classic() +
  theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies (%)", fill = "") +
  scale_fill_manual(values = c("Non-GC" = "#007fff", "GC" = "#ff8033")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Non-GC|\\.GC", "", x))  # Simplify x-axis labels
dev.off()

```


# 20. Break Point (Top 100 features)
## 20.1 colname
```{r}
Breakpoint <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/Feature_names.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(Breakpoint) <- c("Feature_num", "Feature_chr", "Type")

Breakpoint2 <- Breakpoint %>% 
  filter(Type == "Breakpoint")

```

## 20.2 data_Breakpoint
```{r}
# join_data_feature %>%
#   group_by(OS_time) %>%
#   summarise(count = n())

data_Breakpoint <- join_data_feature %>% 
  dplyr::select(Group_predicted, F1207, F1206)
colnames(data_Breakpoint) <- c("Group_predicted", "GCACTT", "GCAGTA")

# write.table(data_Breakpoint, "data_Breakpoint.txt", sep = "\t", row.names = F)

```


# 21. data_Breakpoint plot
```{r}
summary(data_Breakpoint[data_Breakpoint$Group_predicted=="Non-GC",]$GCACTT)
summary(data_Breakpoint[data_Breakpoint$Group_predicted=="GC",]$GCACTT)
p <- wilcox.test(data_Breakpoint[data_Breakpoint$Group_predicted=="Non-GC",]$GCACTT, data_Breakpoint[data_Breakpoint$Group_predicted=="GC",]$GCACTT)
p$p.value

# Reshape data from wide to long format
data_long <- pivot_longer(data_Breakpoint, cols = c(GCACTT, GCAGTA), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("GCACTT.Non-GC", "GCACTT.GC", "GCAGTA.Non-GC", "GCAGTA.GC"))

# Create a list for pairwise comparisons
comparison_list <- list(c("GCACTT.Non-GC", "GCACTT.GC"), 
                        c("GCAGTA.Non-GC", "GCAGTA.GC"))

pdf("20240926_cfDNA_11_Breakpoint_boxplot_v1.pdf", height=4.5, width=4.5)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.5, color = "black", size = 4) + 
  theme_classic() +
  theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies (%)", fill = "") +
  scale_fill_manual(values = c("Non-GC" = "#007fff", "GC" = "#ff8033")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Non-GC|\\.GC", "", x))  # Simplify x-axis labels
dev.off()

```


# 30. Top 100 features
## 30.1 colname
```{r}
feature_100 <- read.xlsx("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/Feature_names.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
colnames(feature_100) <- c("Feature_num", "Feature_chr", "Type")
# feature_100 <- read.csv("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/30_Feature/data_feature_wilcox.csv")
# 
# feature_100_02 <- feature_100 %>%
#   arrange(desc(Fold_Change)) %>%
#   slice(1:50L)
# 
# feature_100_03 <- feature_100 %>%
#   arrange(Fold_Change) %>%
#   slice(1:50L)
# 
# join_feature_100 <- bind_rows(feature_100_02, feature_100_03) %>%
#   distinct()

```

## 30.2 data_feature_100
```{r}
Feature_num <- feature_100$Feature_num
data_feature_100 <- join_data_feature %>%
  dplyr::select(Sample, Group_predicted, feature_100$Feature_num)

# Feature_num <- join_feature_100$Feature
# data_feature_100 <- join_data_feature %>%
#   dplyr::select(Sample, Group_predicted, join_feature_100$Feature)

# write.table(data_feature_100, "data_feature_100.txt", sep = "\t", row.names = F)

```


# 31. data_feature_100 plot
```{r}
data_feature_100 <- data_feature_100 %>% 
  arrange(Group_predicted)

# 保存样本名称和预测组别信息，以便后续使用
sample_info <- data_feature_100[, c("Sample", "Group_predicted")]

# 计算z-score，注意排除第一列（Sample）和Group_predicted列
# data_z <- t(scale(t(data_feature_100[, !names(data_feature_100) %in% c("Sample", "Group_predicted")])))
data_z <- scale(data_feature_100[, !names(data_feature_100) %in% c("Sample", "Group_predicted")], scale = TRUE)

# 转换回数据框，并添加样本和组别信息
data_z <- data.frame(Sample = sample_info$Sample, 
                     Group_predicted = sample_info$Group_predicted, 
                     data_z)

# annotation_row
annotation_row = data.frame(
  Group = factor(data_z$Group_predicted)
)
rownames(annotation_row) = data_z$Sample

# annotation_colors
ann_colors = list(
  Group = c('Non-GC' = "#007fff", 'GC' = "#ff8033")
)

pheatmap_data_z <- data_z %>% 
  select(-Group_predicted) %>%
  column_to_rownames(var = "Sample")

data_z$Group_predicted=factor(data_z$Group_predicted, levels=c('Non-GC', 'GC'))

pdf("20240926_cfDNA_12_feature_100_pheatmap_v1.pdf", height=5, width=10)

pheatmap(pheatmap_data_z, 
         color = colorRampPalette(c("#0000cd","#FFFFFF","#ff3c00"))(100)[0:100], 
         fontsize=9, 
         fontsize_row=9, 
         # display_numbers = matrix(ifelse(copper_pheatmap2 > 1, "*", ""), nrow(copper_pheatmap2)),
         breaks = seq(-5,5,1/10), legend_breaks = seq(-5,5,2.5),
         annotation_row = annotation_row, 
         annotation_colors = ann_colors, 
         cluster_rows=F, 
         cluster_cols=T)
dev.off()

```


# 40. index
## 40.1 colname
```{r}
feature_index <- read.csv("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/data_feature_wilcox_240619.csv")

feature_index2 <- feature_index %>% 
  filter(Type == "INDEX")

```

## 40.2 data_index
```{r}
data_index <- join_data_feature %>% 
  dplyr::select(Group_predicted, F4, F5)
colnames(data_index) <- c("Group_predicted", "Index01", "Index02")

```


# 41. data_index plot
```{r}
summary(data_index[data_index$Group_predicted=="Non-GC",]$Index01)
summary(data_index[data_index$Group_predicted=="GC",]$Index01)
p <- wilcox.test(data_index[data_index$Group_predicted=="Non-GC",]$Index01, data_index[data_index$Group_predicted=="GC",]$Index01)
p$p.value

# Reshape data from wide to long format
data_long <- pivot_longer(data_index, cols = c(Index01, Index02), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("Index01.Non-GC", "Index01.GC", 
                                           "Index02.Non-GC", "Index02.GC"))

# Create a list for pairwise comparisons
comparison_list <- list(c("Index01.Non-GC", "Index01.GC"), 
                        c("Index02.Non-GC", "Index02.GC"))

data_long$Group_predicted=factor(data_long$Group_predicted, levels=c('Non-GC', 'GC'))

pdf("20240926_cfDNA_13_Index_boxplot_v1.pdf", height=4.5, width=4.5)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.5, color = "black", size = 4) + 
  theme_classic() +
  # theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies (%)", fill = "") +
  scale_fill_manual(values = c("Non-GC" = "#007fff", "GC" = "#ff8033")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Non-GC|\\.GC", "", x))  # Simplify x-axis labels
dev.off()

```

# 50. ichorCNA
## 50.1 colname
```{r}
feature_ichorCNA <- read.csv("/Users/xuewei/ZxProjects/20240408_GC_cfDNA/202409/32_AUC/Top100_features/data_feature_wilcox_240619.csv")

feature_ichorCNA2 <- feature_ichorCNA %>% 
  filter(Type == "ichorCNA")

```

## 50.2 data_ichorCNA
```{r}
data_ichorCNA <- join_data_feature %>% 
  dplyr::select(Group_predicted, F8702, F8703)
colnames(data_ichorCNA) <- c("Group_predicted", "CNA01", "CNA02")

```


# 51. data_ichorCNA plot
```{r}
summary(data_ichorCNA[data_ichorCNA$Group_predicted=="Non-GC",]$CNA02)
summary(data_ichorCNA[data_ichorCNA$Group_predicted=="GC",]$CNA02)
p <- wilcox.test(data_ichorCNA[data_ichorCNA$Group_predicted=="Non-GC",]$CNA02, data_ichorCNA[data_ichorCNA$Group_predicted=="GC",]$CNA02)
p$p.value

# Reshape data from wide to long format
data_long <- pivot_longer(data_ichorCNA, cols = c(CNA01, CNA02), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("CNA01.Non-GC", "CNA01.GC", 
                                           "CNA02.Non-GC", "CNA02.GC"))

# Create a list for pairwise comparisons
comparison_list <- list(c("CNA01.Non-GC", "CNA01.GC"), 
                        c("CNA02.Non-GC", "CNA02.GC"))

data_long$Group_predicted=factor(data_long$Group_predicted, levels=c('Non-GC', 'GC'))

pdf("20240926_cfDNA_14_ichorCNA_boxplot_v1.pdf", height=4.5, width=4.5)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.5, color = "black", size = 4) + 
  theme_classic() +
  # theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies (%)", fill = "") +
  scale_fill_manual(values = c("Non-GC" = "#007fff", "GC" = "#ff8033")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Non-GC|\\.GC", "", x))  # Simplify x-axis labels
dev.off()

```

